### 2018-08-07 paper/security-discussion.tex
integrating text from Daniel's uc simulator argument branch

As long as we output all the nodes in the next layer, the results for
the adversary are the same: the adversary learns the entire
composition of the layer regardless of whether the set contains a
single or several nodes.
We note that this is actually quite natural as a malicious adversary can drop 
any incoming traffic to a router and wait for the timeout and retransmission to 
the next node.
As such, the adversary can learn all nodes in the layer.

>>>>

Analogously to traditional \ac{OR},  we also reveal the previous and next sets 
of nodes to the adversary. 
We note that this is actually quite natural as a malicious adversary can drop 
any incoming traffic to a router and wait for the timeout and
retransmission, \ie when the 
node has selected a new node from the next layer and retried sending.
As such, the adversary can learn all nodes in the layer --- just as for 
traditional \ac{OR}, regardless of whether the set making up a layer contains a
single or several nodes.
